### 2012-01-02 doc/pldi2012/circuit.tex

Lines 35-39 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 30-33 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution, nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations
(see Section~\ref{subsec:cirdependence}).

@@

Since a region relationship can have
fields with types that refer to its own fields' regions, it is often not possible
to assign fields one at a time without violating the type checking rules.
The simultaneous assignment operator asks the type checker only to ensure
that fields have the correct types after all the fields are updated.  
Lines 32 and 33 illustrate a simultaneous
assignment to update a {\tt CircuitPiece} region relationship.

>>>>

Lines 36-40 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 30-34 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution, nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations
(see Section~\ref{subsec:cirdependence}).

@@

Since a region relationship can have
fields with types that refer to its own fields' regions, it is often not possible
to assign fields one at a time without violating the type checking rules.
The simultaneous assignment operator asks the type checker only to ensure
that fields have the correct types after all the fields are updated.  In
many cases, the target type also tries to describe tighter constraints on
the region parameters used for field types.  The {\tt region\_cast} operator
allows the programmer to assert the correctness of this transformation, which
can be verified with a linear scan over the elements of a region.
Lines 32-34 illustrate a simultaneous
assignment to update a {\tt CircuitPiece} region relationship.

### 2012-01-02 doc/pldi2012/lowlevel.tex

The final interesting feature of the deferred lock is that it can be associated
with an object in memory and that object will automatically be kept coherent
across the cluster.  This is similar to MESI coherence in a distributed cache,
but is done per-object rather than on cache lines.  This is currently only 
used for objects within the runtime itself, but we are exploring ways to expose
it at the Legion application level.

\subsubsection{Regions}
\label{subsec:regionmeta}
Application-level regions are broken into three inter-related pieces in the
low-level runtime.  The metadata object tracks global information such as
region size and valid mask.  Allocators are used to dynamically allocate and
free entries in a region.  Finally, physical instances hold versions of the data for 
a logical region.

>>>>

%The final interesting feature of the deferred lock is that it can be associated
%with an object in memory and that object will automatically be kept coherent
%across the cluster.  This is similar to MESI coherence in a distributed cache,
%but is done per-object rather than on cache lines.  This is currently only 
%used for objects within the runtime itself, but we are exploring ways to expose
%it at the Legion application level.

\subsubsection{Regions}
\label{subsec:regionmeta}
Application-level regions are broken into three inter-related pieces in the
low-level runtime.  The metadata object tracks global information such as
region size and the set of valid elements, which is used in partitioning
operations.  Allocators are used to dynamically allocate and
free entries in a region.  Finally, physical instances hold versions of the data for 
a logical region.
